\begin{thebibliography}{10}
    \bibitem{carrasquilla2017machine} 
    \textit{Carrasquilla J.} Machine learning phases of matter / 
    J. Carrasquilla, R.G. Melko //
    Neural Netw. -- 2017. -- Vol. 13. -- № 5. -- P. 431--434.
    
    \bibitem{butler2018machine} 
    \textit{Butler K.T.} Machine learning for molecular and materials science / 
    K.T. Butler, D.W. Davies, H. Cartwright, O. Isayev, A. Walsh //
    Nature. -- 2018. -- Vol. 559. -- № 7715. -- P. 547--555.
    
    \bibitem{ceperley1986quantum} 
    \textit{Ceperley D.} Quantum monte carlo / 
    D. Ceperley, B. Alder //
    Science. -- 1986. -- Vol. 231. -- № 4738. -- P. 555--560.
    
    \bibitem{white1992density} 
    \textit{White S.R.} Density matrix formulation for quantum renormalization groups / 
    S.R. White //
    Phys. Rev. Lett. -- 1992. -- Vol. 69. -- № 19. -- P. 2863.
    
    \bibitem{carleo2017solving} 
    \textit{Carleo G.} Solving the quantum many-body problem with artificial neural networks / 
    G. Carleo, M. Troyer //
    Science. -- 2017. -- Vol. 355. -- № 6325. -- P. 602--606.
    
    \bibitem{kolmogorov1956representation} 
    \textit{Колмогоров А.Н.} О представлении непрерывных функций нескольких переменных в виде суперпозиций непрерывных функций одного переменного и сложения / 
    А.Н. Колмогоров //
    ДАН. -- 1957. -- Т. 114. -- № 5. -- P. 953--956.
    
    \bibitem{mcmillan1965ground} 
    \textit{McMillan W.L.} Ground state of liquid He 4 / 
    W.L.McMillan //
    Phys. Rev. -- 1965. -- Vol. 138. -- № 2A. -- P. A442.
    
    \bibitem{ambegaokar2010estimating} 
    \textit{Ambegaokar V.} Estimating errors reliably in Monte Carlo simulations of the Ehrenfest model / 
    V. Ambegaokar, M. Troyer //
    Am. J. Phys. -- 2010. -- Vol. 78. -- № 2. -- P. 150--157.
    
    \bibitem{harju1997stochastic} 
    \textit{Harju A.} Stochastic gradient approximation: An efficient method to optimize many-body wave functions / 
    A. Harju, B. Barbiellini, S. Siljam{\"a}ki, R.M. Nieminen, G. Ortiz //
    Phys. Rev. Lett. -- 1997. -- Vol. 79. -- № 7. -- P. 1173.

    \bibitem{sorella2007weak} 
    \textit{Sorella S.} Weak binding between two aromatic rings: Feeling the van der Waals attraction by quantum Monte Carlo methods / 
    S. Sorella, M. Casula, D.Rocca //
    J. Chem. Phys. -- 2007. -- Vol. 127. -- № 1. -- P. 014105.
    
    \bibitem{hinton2012practical} 
    \textit{Hinton G.E.} A practical guide to training restricted Boltzmann machines / 
    G.E. Hinton //
    Neural networks: Tricks of the trade. -- 2012. -- P. 599--619.
    
    \bibitem{qian1999momentum} 
    \textit{Qian N.} On the momentum term in gradient descent learning algorithms / 
    N. Qian //
    Neural Netw. -- 1999. -- Vol. 12. -- № 1. -- P. 145--151.
    
    \bibitem{kingma2014adam} 
    Adam: A method for stochastic optimization -- URL: \url{https://arxiv.org/abs/1412.6980v8} (дата обращения: 04.04.2020)
    
    \bibitem{duchi2011adaptive} 
    \textit{Duchi J.} Adaptive subgradient methods for online learning and stochastic optimization / 
    J. Duchi, E. Hazan, Y. Singer //
    J. Mach. Learn. Res. -- 2011. -- Vol. 12. -- № Jul. -- P. 2121--2159.
    
    \bibitem{tieleman2012lecture} 
    \textit{Tieleman T.} Lecture 6.5-rmsprop: Divide the gradient by a running average of its recent magnitude / 
    T. Tieleman, G. Hinton //
    COURSERA: Neural networks for machine learning. -- 2012. -- Vol. 4. -- № 2. -- P. 26--31.
    
    \bibitem{konstantinidis2002magnetic} 
    \textit{Konstantinidis N.P.} Magnetic anisotropy in the molecular complex V 15 / 
    N.P. Konstantinidis, D. Coffey //
    Phys. Rev. B. -- 2002. -- Vol. 66. -- № 17. -- P. 174426.
\end{thebibliography}